### 2016-06-09 sec6_spm.tex
Some revisement
Section 4, Section 5 needs to merge

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to achieve a good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we adapt an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsubsection{Star Partition}
The intuition of the star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{spm.eps}
\caption{Star partition and mining of trajectories in Figure~\ref{fig:related_work}}
\label{fig:star_partition}
\end{figure}

@@

\subsubsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

>>>>

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to achieve a good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. 
In SPM, we first design a novel object-based partition 
method named \emph{star partition}. Then, we adapt
an \emph{Apriori} method to mine GCMP patterns
out of each partition.

 The overview of the SPM method 
is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsection{Star Partition}
The intuition of the star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{spm.eps}
\caption{Star partition and mining. (a) Conceptual connection graph from Figure 1.(b) Five star partitions are generated
(c) Apriori Mining with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

@@

\subsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.
